\MakeUppercase{Linear versus centred Colouring Numbers}\thanks{This research was partly funded by NSERC.}

### 2022-04-04 lin-vs-cen.tex
Pffft

>>>>

\section*{Acknowledgement}

The main subject of this paper was posed as an open problem at the 9th Annual Bellairs Workshop on Geometry and Graphs (v2), which was held January 21--28, 2022 and again at the 16th Annual Workshop on Probability and Combinatorics, which was held March 25--April 1, 2022. We are grateful to the organizers and participants of both workshops for providing a stimulating research environment.
